\large \bfseries Asymptotic Capacity of Systems with Intelligent Reflective Surfaces

### 2020-07-06 documentation/Presentations/Mid-Presentation/mid_term_presentation.tex
adding for mid-term presentation

\section{Background}

\begin{frame}
\frametitle{Relaying}

	\begin{itemize}
		\item 			
			Base Stations Vs. Relay $\rightarrow$ reduced core network footprint/cost
%		\item 
%			Modes of operation provide cost/performance trade-off (decode and forward, amplify and forward ...)
		\item 
			Extending wireless coverage is relevant to high frequencies used in 5G +
	\end{itemize}

\begin{frame}
\frametitle{The basic MIMO channel}
Much easier if each channel has a constant frequency response over the relevant band.
	\begin{itemize}
		\item

	\end{itemize}

@@

%\begin{frame}
%\frametitle{IRS: Modes of Operation}
%\begin{columns}
%\begin{column}{0.5\linewidth}
%	Mode 1
%	\begin{figure}
%%			\centering
%		\includegraphics[scale=1]{irs}
%	\end{figure}\end{column}
%\begin{column}{0.5\linewidth}
%	Mode 2 (The one we will use)
%\end{column}
%\end{columns}
%\end{frame}
\begin{frame}
\frametitle{System Model}
\centering
\begin{equation*}
	\mathbf{y} = (\mathbf{H}_2\boldsymbol{\Phi}\mathbf{H}_1 + \mathbf{G})\mathbf{x}
\end{equation*}
with 
$\mathbf{H}_{1}\in \mathbb{C}_{S \times T},\mathbf{H}_{2} \in \mathbb{C}_{R \times S}, \mathbf{G} \in \mathbb{C}_{R \times T}$ and $\boldsymbol{\Phi}$ as $S \times S$ a diagonal matrix with $| \phi_i | =1$.

@@

\section{Goals}
\begin{frame}
\frametitle{Project Goals}
\begin{enumerate}
\item
	Find capacity of asymptotic IRS systems
	\begin{itemize}
	\item 
		Optimize phase matrix
	\item
		Generalize results
	\end{itemize}

\section{Current Status}

>>>>

\section{Background}
\begin{frame}
\frametitle{Massive MIMO}
				\centering
		\begin{figure}
		\includegraphics[scale=.18]{Pictures/mimo_antenna}
	\end{figure}
\end{frame}

\begin{frame}
\frametitle{Simplifying the MIMO Channel: OFDM}
Assuming flat-fading channels between each transmit and receive antenna.
	\begin{itemize}
		\item 			
			Interpret each symbol to be the complex coefficient of a complex sinusoid of specific frequency. 
		\item
			These sinusoids pass through a channel whose frequency response is flat.
		\item
			By considering both channel and transmit signal in the frequency domain, we have a system given by
			\begin{equation}
				\my = \mH \mx.
			\end{equation}
		\item 
			Justify if there are any difficulties for OFDM when moving to the high frequencies required for massive MIMO.
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Channel Correlation}
	\begin{itemize}
		\item 
			FIR filters can represent correlation and their AED can be found. (Can just consider subset for FIR length?)
		\item
			The exponential correlation model is one such FIR filter with a single parameter. (Closed form expression for the S-Transform)
		\item 
			Measurement results for similar models show that $\rho$ can take on values up to $.6$ in $x$ GHz (a band relevant to 5G)
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{System Model}
\centering
\begin{equation*}
	\mathbf{y} = (\mathbf{H}_2\boldsymbol{\Phi}\mathbf{H}+ \mathbf{G})\mathbf{x}
\end{equation*}
with 
$\mathbf{H}_{1}\in \mathbb{C}_{S \times T},\mathbf{H}_{2} \in \mathbb{C}_{R \times S}, \mathbf{G} \in \mathbb{C}_{R \times T}$ and $\boldsymbol{\Phi}$ as $S \times S$ a diagonal matrix with $| \phi_i | =1$.

@@

\begin{frame}
\frametitle{Channel Normalization}
	\begin{itemize}
		\item 
			If transmit power is held constant as $N \rightarrow \infty$, the linear increase in capacity of the MIMO system depends on constant channel statistics.
		\item 
			In order to have a converging AED, we need to normalize the power of the channel.
		\item
			Show how can these results extend to the case without statistics changing? (is this even relevant?)
	\end{itemize}
\end{frame}

\section{Goals}
\begin{frame}
\frametitle{Project Goals}
\begin{enumerate}
\item
	Generalize capacity analysis for a channel model relevant to the IRS.
\item 
	Optimize phase matrix at the IRS (when relevant).
	\begin{itemize}
	\item
		Investigate the cases in which phase optimization is worthwhile. 
	\end{itemize}
\item
	* Time permitting - Consider secrecy capacity of IRS system (phase optimization may be relevant for some cases to increase secrecy capacity).
\item 
	Confirm findings with numerical results throughout.
\end{enumerate}
\end{frame}
\section{Current Status}
